Ultra-deep $K_s$-band Imaging of the \textit{Hubble} Frontier Fields

### 2016-02-25 Paper0/ms.tex
minor change
remove old comment

\xxx\ currently a bit awkward since MOSFIRE reduction done quickly with Ivo's code and HAWK-I done in many additional steps (astrometry and photometry).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Exposure Map figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\epsscale{1.18}
\plotone{hawkiff_layout.pdf} % Figures/exposure_map.pdf
\caption{Layout of the Frontier Fields $K_s$-band mosaics.  The positions of the \textit{HST} cluster and parallel fields are shown in the blue (ACS optical) and red (WFC3 IR) polygons.  The light blue polygons in the MACS-0717 field show additional wide-field ACS imaging coverage from  programs GO-9722 and GO-10420 \citep[PI: Ebeling;][]{ma:11}.  The area covered by deep imaging in the \textit{Spitzer}/IRAC 3.6 and 4.5\,\mum\ channels is shown in orange.  The HAWK-I field of view is perfectly suited (Abell 2744, MACS-0416, Abell S1063 and Abell 370) for simultaneous imaging of the cluster+parallel field pairs, which require two separate pointings with MOSFIRE (MACS-0717 and MACS-1149).  The footprint of additional archival HAWK-I coverage of the MACS-1149 field is indicated by the gray square in the lower right panel.\label{fig:layout}}  
\end{figure*}

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Exposure Map figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\epsscale{1.18}
\plotone{hawkiff_layout.pdf} % Figures/exposure_map.pdf
\caption{Layout of the Frontier Fields $K_s$-band mosaics.  The positions of the \textit{HST} cluster and parallel fields are shown in the blue (ACS optical) and red (WFC3 IR) polygons.  The light blue polygons in the MACS-0717 field show additional wide-field ACS imaging coverage from  programs GO-9722 and GO-10420 \citep[PI: Ebeling;][]{ma:11}.  The area covered by deep imaging in the \textit{Spitzer}/IRAC 3.6 and 4.5\,\mum\ channels is shown in orange, with the cluster fields indicated by the dashed lines.  The HAWK-I field of view is perfectly suited (Abell 2744, MACS-0416, Abell S1063 and Abell 370) for simultaneous imaging of the cluster+parallel field pairs, which require two separate pointings with MOSFIRE (MACS-0717 and MACS-1149).  The footprint of additional archival HAWK-I coverage of the MACS-1149 field is indicated by the gray square in the lower right panel.\label{fig:layout}}  
\end{figure*}
